---
title: "How does it work?"
output:
  pdf_document: default
  html_notebook: default
---

```{r}
library(tidyverse)
library(clusterlab)

normalize <- function(x){((x-min(x))/(max(x)-min(x)))}
```


We are goint yo use the following dataset:

```{r echo=FALSE}
toy_data <- clusterlab(centers = 3,
                        r = 2,
                        numbervec = c(5, 5, 5),
                        sdvec = sample(1:3, 3),
                        alphas = sample(1:3, 3),
                        features = 2,
                        seed = 2020)
toy_data <- as_tibble(t(toy_data$synthetic_data)) %>% 
  mutate(cluster = as.factor(toy_data$identity_matrix$cluster)) %>% 
  mutate_if(is.numeric, normalize)

t(toy_data)
```

```{r echo=FALSE}
ggplot(toy_data, aes(V1, V2, color = cluster)) +
  geom_point()
```

## Assignation



## Update

After the assignation step a dataset with all the data + an additional column
`cluster` containing the cluster to which the object has been assigned is 
available.

Now it is time to update the cluster. 

1. For each distance function $d_\ell$, a matrix $M_{d_\ell}$ containing the distance between
each pair of objects $o_i$ and $o_j$ $d_\ell(o_i,o_j)$ is stored
2. For each cluster $j$, the matrices $M$ are filtered to keep only the points
that belong to the cluster $j$
3. For each point, the distance to all other points is added, obtaining a single number
for each pair of object and distance function
4. The vector containing all the points of the dataset and their respective pair values
are ranked from closest to fruthest
5. Borda account is applied to all the rankings obtained 
6. The borda winner is the one chosen as centroid

The points after the assignation step are:

```{r echo=FALSE}

```

**_Step 1:_**

```{r}

```

**_Step 2:_**

**_Step 3:_**

**_Step 4:_**

**_Step 5:_**

**_Step 6:_**


