---
title: "Distances"
output:
  html_document:
    toc: true
    number_sections: true
    toc_float:
      collapsed: false
      smooth_scroll: false

---

```{r message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
```

```{r warning=FALSE, include=FALSE}
distance_measure <- function(x1, x2, y1, y2) {round(sqrt((x1 - x2) ^ 2 + (y1 - y2) ^ 2), digits = 1)}
add_annotation <- function(index1, index2) {
  x1 <- points[index1, 1] 
  x2 <- points[index2, 1]
  y1 <- points[index1, 2]
  y2 <- points[index2, 2]
  
  list(            
    annotate("segment", color = "blue",
             x = x1, xend = x2,
             y = y1, yend = y2),
    
    annotate("text", color = "black", size = 5,
             x = (x1 + x2) / 2, y = (y1 + y2) / 2,
             label = distance_measure(x1, x2, y1, y2)
    )
  )
}
```

```{r message=FALSE, warning=FALSE, include=FALSE}
set.seed(1234)
points <- as_tibble(t(replicate(10, sample(-5:5, 2))))
colnames(points) <- c("x", "y")
points <- bind_rows(tibble(x = 0, y = 0), points) %>% mutate(class = factor(c("from", rep("to", 10))))
points <- as.data.frame(points)
```

```{r echo=FALSE}
basic_plot <- ggplot(points, aes(x, y)) + 
                geom_point(aes(color = class), size = 5)
basic_plot
```

# $L_p$ Minkowski distance measures

$$d_{\textrm{Minkowski}}\left(x,y\right)=\left(\sum _{i=1}^{n}|x_{i}-y_{i}|^{p}\right)^{1/p}$$

## Manhattan distance

p = 1 

$$d_{\textrm{Manhattan}}\left(x,y\right) = \sum _{i=1}^{n} \left| x_i - y_i \right|$$

## Euclidean distance

p = 2

```{r}
basic_plot + add_annotation(1, 2:11) + 
                geom_point(aes(color = class), size = 5)
```

$$d_{\textrm{Euclidean}}\left(x,y\right) = \sqrt{\sum _{i=1}^{n} \left( x_i - y_i \right)^2}$$

## Chebyshev distance

$$d_{\textrm{Chebyshev}}\left(x,y\right) = \max_i\left| x_i - y_i \right|$$

# $L_1$ distance measures

## Canberra distance

$$d_{\textrm{Canberra}}\left(x,y\right) = \sum _{i=1}^{n} \frac{\left| x_i - y_i \right|}{\left| x_i \right| + \left| y_i \right|} $$

$$d_{\textrm{AverageManhattan}}\left(x,y\right) = \frac{\sum _{i=1}^{n} \left| x_i - y_i \right|}{n} $$

# Inner product distance measures

## Jaccard distance 

$$d_{\textrm{Jaccard}}\left(x,y\right) = \frac{\sum_{i=1}^{n} \left( x_i - y_i \right)^2}{\sum_{i=1}^{n} x_i^2 + \sum_{i=1}^{n} y_i^2 - \sum_{i=1}^{n} x_i y_i} $$

## Cosine distance 

$$d_{\textrm{Jaccard}}\left(x,y\right) = \frac{\sum_{i=1}^{n} x_iy_i}{\sum_{i=1}^{n} x_i^2 + sum_{i=1}^{n} y_i^2 - sum_{i=1}^{n} x_i y_i} $$

# Squared Chord distance measures

## Bhattacharyya
## Matusita

# Squared L2 distance measures

## Clark distance
## Squared x2 distance, a.k.a triangular discrimination distance. This distance is a quasi distance

# Vicissitude distance measures

## Vicis symmetric distance VSD
## Max symmetric x2 distane MiSCSD